\textbf{Discovery of a disrupting open cluster in the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream}

### 2018-11-04 ms.tex
more things

\begin{figure}
\centering
\includegraphics[width=8cm]{orbits.png}
\caption{Integrated orbits (over 60 Myr) of the star cluster using the Gaia DR2 proper motions, the
\hi~velocity and a distance of 25 kpc.  The orbits intersect the MW midplane about
60 Myr ago which is close to the age of the cluster.}
\label{fig_gass}
\end{figure}

>>>>

If we assume that \clustername\ is associated with nearby \hi in the Magellanic stream, we have measurements of all 6 phase-space components of the cluster and can compute orbits for \clustername.
However, as discussed in \sectionname~\ref{sec:higas}, there are two prominent but distinct velocity components of \hi along the line of sight to \clustername.
We therefore integrate orbits of the cluster using both values of the line-of-sight velocity from these two gas components.
\figurename~\ref{fig:orbits}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{orbits.pdf}
\caption{TODO:}
\label{fig:orbits}
\end{figure}
